Lifespan Analysis of Lemurs in Wild and Captive Environments

### 2024-12-15 paper/paper.qmd
Minor detail added in estimand paragraph
ref.bib renamed to references.bib

---
title: "Lifespan Analysis of Lemurs in Wild and Captive Environments"
subtitle: "Evaluating Effective Strategies and Highlighting Areas for Conservation Focus"
author: 
  - Khushaal Nandwani
thanks: "Code and data are available at: [https://github.com/khushaal-nandwani/predicting-lemurs/tree/main](https://github.com/khushaal-nandwani/predicting-lemurs/tree/main)."
date: today
date-format: long
abstract: "This study investigates the lifespan of lemurs in wild and captive environments using data from the Duke Lemur Center, aiming to identify how factors such as sex, species, genus, and birth month influence longevity. Using Generalized Linear Models, the analysis found that lemurs in captivity live significantly longer than their wild counterparts, emphasizing the impact of conservation practices. The study also identified species-specific variations in lifespan and a pronounced influence of sex in captivity. The findings from this study can help determine what we are doing right and where we are going wrong."
format: pdf
number-sections: true
toc: true
bibliography: ref.bib
# editor:
#   render-on-save: true
---
```{r}
#| echo: false
#| warning: false
#| message: false
library(tidyverse)  
library(ggplot2)
library(dplyr)
library(patchwork) # For arranging plots side by side
library(arrow)
library(kableExtra)
library(rstanarm)
library(knitr)

@@

The estimand for our model is the age or the lifespan of the lemur. The predictors are `Sex`, `Species`, `Genus`, and `month_born`.

>>>>

---
title: "Lifespan Analysis of Lemurs in Wild and Captive Environments"
subtitle: "Evaluating Effective Strategies and Highlighting Areas for Conservation Focus"
author: 
  - Khushaal Nandwani
thanks: "Code and data are available at: [https://github.com/khushaal-nandwani/predicting-lemurs/tree/main](https://github.com/khushaal-nandwani/predicting-lemurs/tree/main)."
date: today
date-format: long
abstract: "This study investigates the lifespan of lemurs in wild and captive environments using data from the Duke Lemur Center, aiming to identify how factors such as sex, species, genus, and birth month influence longevity. Using Generalized Linear Models, the analysis found that lemurs in captivity live significantly longer than their wild counterparts, emphasizing the impact of conservation practices. The study also identified species-specific variations in lifespan and a pronounced influence of sex in captivity. The findings from this study can help determine what we are doing right and where we are going wrong in our conservation efforts for this endangered species."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
# editor:
#   render-on-save: true
---
```{r}
#| echo: false
#| warning: false
#| message: false
library(tidyverse)  
library(ggplot2)
library(dplyr)
library(patchwork) # For arranging plots side by side
library(arrow)
library(kableExtra)
library(rstanarm)
library(knitr)

@@

The estimand for our model is the age or the lifespan of the lemur in wild and captive enviornments. The predictors are `Sex`, `Species`, `Genus`, and `month_born`.
